Classless Java: Tuning Java Interfaces

### 2015-12-02 paper/sections/Formalization.tex
small change in S3

\subsection{Classifying Method Composition}
When interfaces are composed and methods with the same name (and
signature) exist, there are 3 possible outcomes.
We illustrate the possible outcomes using the following (correct) declarations:
\begin{lstlisting}
interface A1{T m(); }
interface A2 extends A1{default T m(){ ... } }
interface A3 extends A2{T m(); }

>>>>

\subsection{Classifying Outcomes of Interface Composition}
When interfaces are composed and methods with the same name (and
signature) exist, there are 3 possible outcomes.
We illustrate the possible outcomes using the following (correct) declarations:
\begin{lstlisting}
interface A1{T m(); }
interface A2 extends A1{default T m(){ ... } }
interface A3 extends A2{T m(); }
